\normalsize{A general approach and tool to evaluate the effectiveness of no-take marine reserves}

### 2017-08-17 Manuscript.Rmd
Aded plos csl and updated author list and affiliations

---
title: \normalsize{A general approach and tool to evaluate the effectiveness of no-take marine reserves}
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
# csl: plos.csl
---

@@

Juan Carlos Villaseñor-Derbez^1\*^, Caio Faro^1^, Melaina Wright^1^, Jael Martínez^1^, Alvin Suárez^2^, Stuart Fulton^2^, Sean Fitzgerald^1^, Gavin McDonald^4^, Jorge Torre-Cosio^2^, Fiorenza Micheli^3^, Christopher Costello^1,4^ \

@@

^3^ Hopkins Marine Station, Stanford University, Monterey, California, United States

^4^ Sustainable Fisheries Group, University of California Santa Barbara, Santa Barbara, California, United States \

>>>>

---
title: \normalsize{A general approach and tool to evaluate the effectiveness of no-take marine reserves}
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
csl: plos.csl
---

@@

Juan Carlos Villaseñor-Derbez^1\*^, Caio Faro^1^, Melaina Wright^1^, Jael Martínez^1^, Sean Fitzgerald^1^, Stuart Fulton^2^, Maria del Mar Mancha-Cisneros^3^, Gavin McDonald^1,4,5^, Fiorenza Micheli^6^, Alvin Suárez^2^, Jorge Torre^2^, Christopher Costello^1,4,5^

@@

^3^ School of Life Sciences, Arizona State University, Tempe, Arizona, United States

^4^ Sustainable Fisheries Group, University of California Santa Barbara, Santa Barbara, California, United States

^5^ Marine Science Institute, University of California Santa Barbara, Santa Barbara, California, United States

^6^ Hopkins Marine Station and Center for Ocean Solutions, Stanford University, Pacific Grove, CA 93950, USA
